---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
packages
```{r}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(randomForest)
library(caret)#predictor diagnostics 
library(e1071)#for caret
library(pdp)
library(VSURF)
```

Load file 
```{r}
data = read.csv("CleanAnalysisData.csv")
```

Carbon flux with site variables

```{r}
rf.c = randomForest(auc.f ~ soil.age + mb.c + meann + meanc + C.N + mb.cn + meanmb + lat_start + long_start + ecoregion + moisture_class + elev + slope + org_layer_depth_transect + density_picea_mariana + age_stand, data = data)
rf.c
plot(rf.c)

train(auc.f ~ soil.age + mb.c + meann + meanc + C.N + mb.cn + meanmb + lat_start + long_start + ecoregion + moisture_class + elev + slope + org_layer_depth_transect + density_picea_mariana + age_stand, data = data)

rf.c = randomForest(auc.f ~ soil.age + mb.c + meann + meanc + C.N + mb.cn + meanmb + lat_start + long_start + ecoregion + moisture_class + elev + slope + org_layer_depth_transect + density_picea_mariana + age_stand, data = data)

rf.c
varImp(rf.c, scale = FALSE)
varImpPlot(rf.c)


rf.c1 = randomForest(auc.f ~ soil.age + C.N + meanc + meanmb, data = data, mtry = 2, importance = T, mode = "regression")

rf.c1
varImpPlot(rf.c1)
importance(rf.c1)
varImp(rf.c1, scale = FALSE)
```
model explains around 60% of variance

partial dependence plots for top 4 variables
```{r}
par.c <- partial(rf.c1, pred.var = c("meanc"), chull = TRUE)
plot.c <- autoplot(par.c, contour = TRUE)

par.mb <- partial(rf.c1, pred.var = c("meanmb"), chull = TRUE)
plot.mb <- autoplot(par.mb, contour = TRUE)

par.soil <- partial(rf.c1, pred.var = c("soil.age"), chull = TRUE)
plot.soil <- autoplot(par.soil, contour = TRUE)

par.cn <- partial(rf.c1, pred.var = c("C.N"), chull = TRUE)
plot.cn <- autoplot(par.cn, contour = TRUE)

grid.arrange(plot.mb, plot.soil, plot.c, plot.cn)
```

vsurf work
```{r}
data1 = select(data, c("auc.f", "soil.age", "meann", "meanc", "C.N", "meanmb", "mb.cn", "mb.c", "lat_start", "long_start", "ecoregion", "moisture_class", "elev", "slope", "org_layer_depth_transect", "density_picea_mariana", "age_stand"))
```

vsurf model
```{r}
cflux.vsurf <- VSURF(data1[,2:17], data1[,1], ntree = 100, nfor.thres = 20, nfor.interp = 10, nfor.pred = 10)
cflux.vsurf
cflux.vsurf$varselect.thres
cflux.vsurf$varselect.interp
cflux.vsurf$varselect.pred

plot(cflux.vsurf)
plot(cflux.vsurf$varselect.pred, var.names = TRUE)
```
vsurf in order of importance = microbial biomass, soil age, %C, C/N

Nitrogen mineralization with site variables

All variables included 5% variance explained. Simplified model and explains a little less, 3%. Nitrogen mineralization is hard.
```{r}
rf.n = randomForest(min.n ~ mb.c + soil.age + meanc + meann + meanmb + C.N + lat_start + long_start + ecoregion + moisture_class + elev + slope + org_layer_depth_transect + density_picea_mariana + age_stand, data = data)
rf.n
plot(rf.n)

train(min.n ~ mb.c + auc.f + soil.age + meanc + meann + meanmb + C.N + lat_start + long_start + ecoregion + moisture_class + elev + slope + org_layer_depth_transect + density_picea_mariana + age_stand, data = data)


rf.n = randomForest(min.n ~ mb.c + soil.age + meanc + meann + meanmb + C.N + lat_start + long_start + ecoregion + moisture_class + elev + slope + org_layer_depth_transect + density_picea_mariana + age_stand, data = data, mtry = 2, importance = T, mode = "regression")
rf.n

varImpPlot(rf.n)

rf.n1 = randomForest(min.n ~ org_layer_depth_transect + meanmb + mb.c + soil.age, data = data, mtry = 2, importance = T, mode = "regression")
rf.n1

varImpPlot(rf.n1)
importance(rf.n1)
varImp(rf.n1, scale = FALSE)
```

partail dependence N min. basically useless
```{r}
par.soil <- partial(rf.n1, pred.var = c("mb.c"), chull = TRUE)
plot.soil <- autoplot(par.soil, contour = TRUE)

par.stand <- partial(rf.n1, pred.var = c("soil.age"), chull = TRUE)
plot.stand <- autoplot(par.stand, contour = TRUE)

par.depth <- partial(rf.n1, pred.var = c("auc.f"), chull = TRUE)
plot.depth <- autoplot(par.depth, contour = TRUE)

grid.arrange(plot.soil, plot.stand, plot.depth)
```

```{r}
data2 = select(data, c("min.n", "soil.age", "meann", "meanc", "C.N", "meanmb", "mb.cn","mb.c", "lat_start", "long_start", "ecoregion", "moisture_class", "elev", "slope", "org_layer_depth_transect", "density_picea_mariana", "age_stand", "auc.f"))
```

```{r}
nmin.vf <- VSURF(data2[,2:18], data1[,1], ntree = 100, nfor.thres = 20, nfor.interp = 10, nfor.pred = 10)
nmin.vf
nmin.vf$varselect.thres
nmin.vf$varselect.interp
nmin.vf$varselect.pred
```
C flux is th only parameter used

Respired C age

Same thing, ran 5 times, microbes, soil age, flux, and bs density in top. before reduction explained ~15 after ~20%
```{r}
data3 = na.omit(data)

rf.res = randomForest(res.age ~ mb.c + soil.age + meanc + C.N + lat_start + long_start + ecoregion + moisture_class + elev + slope + org_layer_depth_transect + density_picea_mariana + age_stand, data = data3, importance = T, mode = "regression")
rf.res

train(res.age ~ mb.c + soil.age + meanc + C.N + lat_start + long_start + ecoregion + moisture_class + elev + slope + org_layer_depth_transect + density_picea_mariana + age_stand + auc.f, data = data3)

rf.res = randomForest(res.age ~ mb.c + soil.age + meanc + C.N + lat_start + long_start + ecoregion + moisture_class + elev + slope + org_layer_depth_transect + density_picea_mariana + age_stand , data = data3, mtry = 2, importance = T, mode = "regression")
rf.res

varImpPlot(rf.res)

rf.res1 = randomForest(res.age ~ mb.c + soil.age + org_layer_depth_transect + density_picea_mariana, data = data3, mtry = 2, importance = T, mode = "regression")
rf.res1

varImpPlot(rf.res1)
importance(rf.res1)
varImp(rf.res1, scale = FALSE)
```

partial dependency respired age
```{r}
par.soil <- partial(rf.res1, pred.var = c("meanmb"), chull = TRUE)
plot.soil <- autoplot(par.soil, contour = TRUE)

par.cn <- partial(rf.res1, pred.var = c("auc.f"), chull = TRUE)
plot.cn <- autoplot(par.cn, contour = TRUE)

par.stand <- partial(rf.res1, pred.var = c("soil.age"), chull = TRUE)
plot.stand <- autoplot(par.stand, contour = TRUE)

par.depth <- partial(rf.res1, pred.var = c("org_layer_depth_transect"), chull = TRUE)
plot.depth <- autoplot(par.depth, contour = TRUE)

grid.arrange(plot.soil, plot.stand, plot.cn, plot.depth)
```

```{r}
data3 = select(data, c("res.age", "soil.age", "meann", "meanc", "C.N", "mb.cn","meanmb", "mb.c", "lat_start", "long_start", "ecoregion", "moisture_class", "elev", "slope", "org_layer_depth_transect", "density_picea_mariana", "age_stand", "auc.f", "min.n"))
data3 = na.omit(data3)
```

```{r}
res.vf <- VSURF(data3[,2:18], data3[,1], ntree = 100, nfor.thres = 20, nfor.interp = 10, nfor.pred = 10)
res.vf
res.vf$varselect.thres
res.vf$varselect.interp
res.vf$varselect.pred
```
C flux is the only parameter

turnover time
```{r}
rf.to = randomForest(tover ~ soil.age + mb.c + meann + meanc + C.N + mb.cn + meanmb + lat_start + long_start + ecoregion + moisture_class + elev + slope + org_layer_depth_transect + density_picea_mariana + age_stand, data = data)
rf.to
plot(rf.to)

train(tover ~ soil.age + mb.c + meann + meanc + C.N + mb.cn + meanmb + lat_start + long_start + ecoregion + moisture_class + elev + slope + org_layer_depth_transect + density_picea_mariana + age_stand, data = data)

rf.to = randomForest(tover ~ soil.age + mb.c + meann + meanc + C.N + mb.cn + meanmb + lat_start + long_start + ecoregion + moisture_class + elev + slope + org_layer_depth_transect + density_picea_mariana + age_stand, data = data, mtry = 15, importance = T, mode = "regression")

rf.to
varImpPlot(rf.to)

rf.to1 = randomForest(tover ~ meanc + C.N + meann + soil.age, data = data, mtry = 4, importance = T, mode = "regression")

rf.to1
varImpPlot(rf.to1)
importance(rf.to1)
varImp(rf.to1, scale = FALSE)
```

partial dependency turnover *****NOT EDITTED*****
```{r}
par.soil <- partial(rf.res1, pred.var = c("meanmb"), chull = TRUE)
plot.soil <- autoplot(par.soil, contour = TRUE)

par.cn <- partial(rf.res1, pred.var = c("auc.f"), chull = TRUE)
plot.cn <- autoplot(par.cn, contour = TRUE)

par.stand <- partial(rf.res1, pred.var = c("soil.age"), chull = TRUE)
plot.stand <- autoplot(par.stand, contour = TRUE)

par.depth <- partial(rf.res1, pred.var = c("org_layer_depth_transect"), chull = TRUE)
plot.depth <- autoplot(par.depth, contour = TRUE)

grid.arrange(plot.soil, plot.stand, plot.cn, plot.depth)
```