---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

This is linear mixed modeling portion of NWT incubation analysis

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(lme4)
library(lmerTest)
library(MuMIn)
library(nlme)
```

Clean data made in other R scripts this is all need
```{r}
data = read.csv("CleanAnalysisData.csv")
```

Lets start by looking at all the C flux data. 
soil age, microbes, C/N
```{r}
tot.f <-lmer(auc.f ~ soil.age * C.N * mb.c + (1| fire), na.action=na.exclude, data = data)
anova(tot.f)
tot.f1 <-lmer(auc.f ~ soil.age * C.N + mb.c + (1| fire), na.action=na.exclude, data = data)
anova(tot.f, tot.f1)
tot.f2 <-lmer(auc.f ~ soil.age + C.N + mb.c + (1| fire), na.action=na.exclude, data = data)
anova(tot.f2, tot.f1)
anova(tot.f2)
tot.f3 <-lmer(auc.f ~ soil.age + mb.c + (1| fire), na.action=na.exclude, data = data)
anova(tot.f2, tot.f3)
tot.f4 <-lmer(auc.f ~ soil.age + (1| fire), na.action=na.exclude, data = data)
anova(tot.f4, tot.f3)

plot(tot.f3)
r.squaredGLMM(tot.f3)
anova(tot.f3)
```
tot.f3 is final soil age + microbial

graph
```{r}
ggplot(data, aes(x = soil.age, y = auc.f)) +
geom_point(size = 4) +
theme_bw(base_size = 22)+
scale_y_continuous(expression("Total C" *O[2]* " lost (mg C/ g C) ")) +
xlab(expression("Bulk soil "*paste(Delta^{14}, "C (‰)"))) +
geom_smooth(method="lm", formula= y ~ x, se=T, color=1) 

ggplot(data, aes(x = mb.c, y = auc.f)) +
geom_point(size = 4) +
theme_bw(base_size = 22)+
geom_abline(slope = 0,intercept = 0) +
xlab("Microbial biomass (µg C/ g C)") +
scale_y_continuous(expression("Total C" *O[2]* " lost (mg C/ g C) ")) +
stat_smooth(method = "lm", formula = y ~ x, color=1)
```


N mineralization
```{r}
nitro <-lmer(min.n ~ soil.age * C.N * mb.c + (1| fire), na.action=na.exclude, data = data)
nitro1 <-lmer(min.n ~ soil.age * C.N + mb.c + (1| fire), na.action=na.exclude, data = data)
anova(nitro, nitro1)
nitro2 <-lmer(min.n ~ soil.age + C.N + mb.c + (1| fire), na.action=na.exclude, data = data)
anova(nitro2, nitro1)
anova(nitro2)
nitro3 <-lmer(min.n ~ C.N + mb.c + (1| fire), na.action=na.exclude, data = data)
anova(nitro2, nitro3)
anova(nitro3)
nitro4 <-lmer(min.n ~ mb.c + (1| fire), na.action=na.exclude, data = data)
anova(nitro4, nitro3)
nitro5 <-lmer(min.n ~ C.N + (1| fire), na.action=na.exclude, data = data)

nitro6 <-lmer(min.n ~ 1 + (1| fire), na.action=na.exclude, data = data)
anova(nitro5, nitro6)
anova(nitro4, nitro5, nitro6)
```
Use model nitro4; mineralization is controlled by microbial biomass

Graph mineralization
```{r}
ggplot(data, aes(y = min.n, x = mb.c)) +
geom_point(size = 4) +
theme_bw(base_size = 22)+
scale_x_continuous(expression("Microbial biomass (µg C "*g^-1*"C)")) +
scale_y_continuous(expression("Net N mineralized (µg N "*g^-1*"N)")) +
stat_smooth(method = "lm", formula = y ~ x, color=1)
```

```{r}
res <-lmer(res.age ~ soil.age * C.N * mb.c + (1| fire), na.action=na.exclude, data = data)
anova(res)
res1 <-lmer(res.age ~ soil.age * C.N + mb.c + (1| fire), na.action=na.exclude, data = data)
anova(res, res1)
res2 <-lmer(res.age ~ soil.age + C.N + mb.c + (1| fire), na.action=na.exclude, data = data)
anova(res2, res1)
res3 <-lmer(res.age ~ soil.age + mb.c + (1| fire), na.action=na.exclude, data = data)
anova(res2, res3)
anova(res3)
res4 <-lmer(res.age ~ soil.age + (1| fire), na.action=na.exclude, data = data)
anova(res4, res3)
res5 <-lmer(res.age ~ mb.c + (1| fire), na.action=na.exclude, data = data)
anova(res5, res3)


```


```{r}
ggplot(data, aes(x = soil.age, y = res.age)) +
geom_point(size = 4) +
theme_bw(base_size = 22)+
xlab(expression("Bulk soil "*paste(Delta^{14}, "C (‰)"))) +
ylab(expression("Respired "*paste(Delta^{14}, "C (‰)"))) +
stat_smooth(method = "lm", formula = y ~ x, color=1)

ggplot(data, aes(x = mb.c, y = res.age)) +
geom_point(size = 4) +
theme_bw(base_size = 22)+
scale_x_continuous(expression("Microbial biomass (µg C "*g^-1*"C)")) +
ylab(expression("Respired "*paste(Delta^{14}, "C (‰)"))) +
stat_smooth(method = "lm", formula = y ~ x, color=1)
```


```{r}
```



out of order but N over time with
a little data wrangling to start

```{r}
n.time = read.csv("N_time.csv")
data1 = merge(n.time, data, by = c("sample", "plot", "fire"))

data1$doi = as.factor(data1$doi)
```

NONE of the variables are controlled by soil age. Some are by time (DIN and ammonium)

DIN over time with soil age
```{r}
ctrl <- lmeControl(opt='optim') 
n.din <-lmer(din ~ soil.age * doi + (1| fire) + (1| sample), na.action=na.exclude, data = data1)
anova(n.din)
n.din1 <-lmer(din ~ soil.age + doi + (1| fire) + (1| sample), na.action=na.exclude, data = data1)
anova(n.din, n.din1)

n.din2 <-lmer(din ~ soil.age + (1| fire) + (1| sample), na.action=na.exclude, data = data1)
anova(n.din1, n.din2)

n.din3 <-lmer(din ~ doi + (1| fire) + (1| sample), na.action=na.exclude, data = data1)
anova(n.din1, n.din3)
n.din4 <-lmer(din ~ 1 + (1| fire) + (1| sample), na.action=na.exclude, data = data1)
anova(n.din3, n.din4)

anova(n.din3)
plot(n.din3)
#need to log transform. but we dont really care the din changes throught time we know that
r.squaredGLMM(n.din3)
```

Ammonium nh4
```{r}
n.nh4 <-lmer(nh4 ~ soil.age * doi + (1| fire) + (1| sample), na.action=na.exclude, data = data1)
n.nh41 <-lmer(nh4 ~ soil.age + doi + (1| fire) + (1| sample), na.action=na.exclude, data = data1)
anova(n.nh4, n.nh41)

n.nh42 <-lmer(nh4 ~ doi + (1| fire) + (1| sample), na.action=na.exclude, data = data1)
anova(n.nh42, n.nh41)

n.nh43 <-lmer(nh4 ~ 1 + (1| fire) + (1| sample), na.action=na.exclude, data = data1)
anova(n.nh42, n.nh43)

anova(n.nh42)
plot(n.nh42)
#need to log transform
n.nh44 <-lmer(log(nh4) ~ doi + (1| fire) + (1| sample), na.action=na.exclude, data = data1)
plot(n.nh44)
r.squaredGLMM(n.nh42)
```

Nitrate no3
```{r}
n.no3 <-lmer(no3 ~ soil.age * doi + (1| fire) + (1| sample), na.action=na.exclude, data = data1)
n.no31 <-lmer(no3 ~ soil.age + doi + (1| fire) + (1| sample), na.action=na.exclude, data = data1)
anova(n.no3, n.no31)

n.no32 <-lmer(no3 ~ doi + (1| fire) + (1| sample), na.action=na.exclude, data = data1)
anova(n.no32, n.no31)

n.no33 <-lmer(no3 ~ 1 + (1| fire) + (1| sample), na.action=na.exclude, data = data1)
anova(n.no32, n.no33)
```
Nitrate isnt predicted by time (doi)
