---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(lme4)
library(lmerTest)
library(MuMIn)
library(nlme)
```

Load files with flux and C and N concentration
```{r}
cn = read.csv("CN.csv")
flux = read.csv("All_flux.csv")
flux.cn = merge(flux, cn, by = c("sample"))
```

load nitrogen and microbial data
```{r}
net.n = read.csv("net_nitrogen.csv")
mb.nitro = read.csv("MB_DIN.csv")
```

load soil and respired age data
```{r}
legacy = read.csv("legacy.csv")
res = read.csv("legacy_res.csv")
```

make one huge dataframe 
THIS IS A FUCKING MESS but IT WORKS
```{r}
flux1 = flux %>%
  group_by(plot, sample) %>%
  summarise(mean.flux = mean(flux,  na.rm = TRUE))

flux2 = flux1 %>%
  group_by(plot, sample) %>%
  mutate(total.flux = mean.flux * 90)

flux.net = merge(flux2, net.n, by = c("sample", "plot"))

flux.net1 = flux.net %>%
  group_by(fire, plot, sample) %>%
  mutate(net.n = mean(net.din, na.rm = TRUE))

c1 = flux.cn %>% 
  group_by(sample, plot) %>% 
  summarize(meanc = mean(carbon, na.rm=TRUE))  
  ungroup()

n1 = flux.cn %>% 
  group_by(sample, plot) %>% 
  summarize(meann = mean(nitrogen, na.rm=TRUE)) 
  ungroup()
  
meancn = merge(n1, c1, by = c("sample", "plot"))
meancn = meancn %>% 
  mutate(C.N = meanc/meann)

flux.net2 = merge(flux.net1, flux1, by = c( "sample", "plot"))

flux.net.leg = merge(flux.net2, legacy, by = c( "sample", "plot"))

flux.net.res = merge(flux.net.leg, res, by = c( "sample", "plot"), all.x = TRUE)

mb = mb.nitro %>%
  group_by(fire, plot, sample) %>%
  summarise(meanmb = mean(mbc,  na.rm = TRUE))

all = merge(flux.net.leg, flux.net.res, by = c("plot" , "fire"), all.x = TRUE)

all = select(all, c("fire", "plot", "sample.x", "mean.flux.x.x", "total.flux.x", "net.nit.x", "net.din.x", "type.x", "D14C.x", "type.y", "D14C.y"))

all = all %>% rename(sample = sample.x, mean.flux = mean.flux.x.x, t.flux = total.flux.x, net.nit = net.nit.x, net.din =  net.din.x, soil.del = type.x, soil.age = D14C.x, res.del = type.y, res.age = D14C.y)

all1 = merge(all, meancn, by = c("sample", "plot"))
all2 = merge(all1, mb, by = c("fire", "sample", "plot"))

all3 = unique(all2)

full = all3 %>%
  filter( !is.na(net.nit))

#remove sample, was mostly mineral soil and below 20% cuttoff for organic
full = full[-c(39), ] 
```

Add new variables C flux per unit C and C flux per unit microbial biomass and N
```{r}
#per C
full1 = full %>%
  group_by(fire, plot, sample) %>%
  mutate(flux.c = mean.flux/meanc)
#per N
full1 = full1 %>%
  group_by(fire, plot, sample) %>%
  mutate(min.n = net.din/meann)
```

```{r}
#per Microbial bio for activity
full1 = full1 %>%
  group_by(fire, plot, sample) %>%
  mutate(flux.mb = meanmb/flux.c)
#per microbial per g C
full1 = full1 %>%
  group_by(fire, plot, sample) %>%
  mutate(mb.c = meanmb/meanc)
```

```{r}
write.csv(full1, "nwtCalcVar.csv")
```

looking at soil age x flux first
mean.flux is skewed and log transforming it makes it normal
```{r}
ggplot()+
  geom_histogram(data=full, aes(mean.flux))
ggplot()+
  geom_histogram(data=full, aes(log(mean.flux)))
ggplot()+
  geom_histogram(data=full, aes(poly(soil.age)))
ggplot()+
  geom_histogram(data=full, aes(soil.age))

ctrl <- lmeControl(opt='optim') 

logf <-lmer(log(mean.flux) ~ soil.age + (1| fire), na.action=na.exclude, data = full)
summary(logf)
plot(logf)
r.squaredGLMM(logf)
anova(logf)

logf1 <-lmer(mean.flux ~ 1 + (1| fire), na.action=na.exclude, data = full)
summary(logf1)
anova(logf1)
anova(logf, logf1)
r.squaredGLMM(logf1)

ggplot(full, aes(x = soil.age, y = log(mean.flux))) +
geom_point(size = 2) +
theme_bw(base_size = 22)+
geom_abline(slope = 0,intercept = 0) +
scale_y_continuous(expression("log(mean flux (µg C" *O[2]* "-C "  *  g^-1*"soil))")) +
xlab(expression("Bulk soil "*paste(Delta^{14}, "C (‰)"))) +
geom_smooth(method="lm", formula= y ~ x, se=T, color=1)
```

flux g C x soil age
same results as just flux without log transforming
use this flux g C instead of soil throughout. Easier to interpret and follow takes the amount of C in sample out of picture and is less confounding
```{r}
ctrl <- lmeControl(opt='optim') 

fc <-lmer(flux.c ~ soil.age + (1| fire), na.action=na.exclude, data = full1)
summary(fc)
plot(fc)
r.squaredGLMM(fc)
anova(fc)

fc1 <-lmer(flux.c ~ 1 + (1| fire), na.action=na.exclude, data = full1)
summary(fc1)
anova(fc1)
anova(fc, fc1)

ggplot(full1, aes(x = soil.age, y = flux.c)) +
geom_point(size = 4) +
theme_bw(base_size = 22)+
scale_y_continuous(expression("Mean flux (µg C" *O[2]* "-C "  *  g^-1*"C)")) +
xlab(expression("Bulk soil "*paste(Delta^{14}, "C (‰)"))) +
geom_smooth(method="lm", formula= y ~ x, se=T, color=1) 
```

flux x mineralization and nitrate
```{r}
ggplot()+
  geom_histogram(data=full, aes(net.din))
ggplot()+
  geom_histogram(data=full, aes(mean.flux))
ggplot()+
  geom_histogram(data=full, aes(log(mean.flux)))

ctrl <- lmeControl(opt='optim') 
nf <-lme(net.din ~ 1,  random=~ 1|fire, method  ="ML", control=ctrl, data=full, na.action=na.exclude)
summary(nf)
anova(nf)

nf1 <-lme(net.din ~ mean.flux,  random=~ 1|fire, method  ="ML", control=ctrl, data=full, na.action=na.exclude)
summary(nf1)
anova(nf, nf1)

nflog <-lme(net.din ~ log(mean.flux),  random=~ 1|fire, method  ="ML", control=ctrl, data=full, na.action=na.exclude)
summary(nflog)
anova(nf1, nflog)
anova(nf1)
r.squaredGLMM(nf1)
plot(nf1)

ggplot(full1, aes(y = net.din, x = mean.flux)) +
  geom_point(aes(colour = soil.age), size = 5) +
  scale_color_continuous(low = "black", high = "green" ) +
  guides(col=guide_legend(expression("Bulk soil "*paste(Delta^{14}, "C (‰)"))))+
  theme_bw(base_size = 22)+
scale_y_continuous(expression("Net N mineralized (µg N "*g^-1*"soil)")) +
scale_x_continuous(expression("Mean flux (µg C" *O[2]* "-C "  *  g^-1*"C)")) +
stat_smooth(method = "lm", formula = y ~ x, color = 1) 

#nitrate starts here
ctrl <- lmeControl(opt='optim') 
nn <-lme(net.nit ~ 1,  random=~ 1|fire, method  ="ML", control=ctrl, data=full, na.action=na.exclude)
summary(nn)

nn1 <-lme(net.nit ~ mean.flux,  random=~ 1|fire, method  ="ML", control=ctrl, data=full, na.action=na.exclude)
summary(nn1)
anova(nn, nn1)

####not significant
ggplot(full, aes(y = net.nit, x = mean.flux)) +
geom_point() +
theme_bw(base_size = 30)+
ylab("Net Nitrate mineralized (µg N/g dry soil)") +
xlab(expression("Mean C" *O[2]* " flux")) +
stat_smooth(method = "lm", formula = y ~ x, size = 2, se = FALSE)
```

flux and minerlaization gram C and gram N
```{r}
ctrl <- lmeControl(opt='optim') 
car <-lme(min.n ~ 1,  random=~ 1|fire, method  ="ML", control=ctrl, data=full1, na.action=na.exclude)

car1 <-lme(min.n ~ flux.c,  random=~ 1|fire, method  ="ML", control=ctrl, data=full1, na.action=na.exclude)
anova(car1)
anova(car, car1)

car2 <-lme(min.n ~ flux.c + soil.age,  random=~ 1|fire, method  ="ML", control=ctrl, data=full1, na.action=na.exclude)
anova(car2)
anova(car2, car1)

ggplot(full1, aes(y = min.n, x = flux.c)) +
  geom_point( size = 4) +
 # scale_color_continuous(low = "black", high = "green" ) +
  #guides(col=guide_legend(expression("Bulk soil "*paste(Delta^{14}, "C (‰)"))))+
  theme_bw(base_size = 22)+
scale_y_continuous(expression("Net N mineralized (µg N "*g^-1*"N)")) +
scale_x_continuous(expression("Mean flux (µg C" *O[2]* "-C "  *  g^-1*"C)")) +
stat_smooth(method = "lm", formula = y ~ x, color = 1) 

#cant use this graph age not significant with n min and flux
ggplot(full1, aes(y = min.n, x = flux.c)) +
  geom_point(aes(colour = soil.age), size = 5) +
  scale_color_continuous(low = "black", high = "green" ) +
  guides(col=guide_legend(expression("Bulk soil "*paste(Delta^{14}, "C (‰)"))))+
  theme_bw(base_size = 22)+
scale_y_continuous(expression("Net N mineralized (µg N "*g^-1*"N)")) +
scale_x_continuous(expression("Mean flux (µg C" *O[2]* "-C "  *  g^-1*"C)")) 
```


flux per C (not like soil as above) x mineralization and nitrate
same results as per g soil
```{r}
ggplot()+
  geom_histogram(data=full1, aes(net.din))
ggplot()+
  geom_histogram(data=full1, aes(flux.c))

ctrl <- lmeControl(opt='optim') 
car <-lme(net.din ~ 1,  random=~ 1|fire, method  ="ML", control=ctrl, data=full1, na.action=na.exclude)
summary(car)
anova(car)

car1 <-lme(net.din ~ flux.c,  random=~ 1|fire, method  ="ML", control=ctrl, data=full1, na.action=na.exclude)
summary(car1)
anova(car, car1)
anova(car1)
plot(car1)

carlog <-lme(net.din ~ log(flux.c),  random=~ 1|fire, method  ="ML", control=ctrl, data=full1, na.action=na.exclude)
summary(carlog)
anova(car1, carlog)
anova(carlog)
r.squaredGLMM(carlog)
plot(carlog)

ggplot(full1, aes(y = net.din, x = flux.c)) +
geom_point(size = 2) +
theme_bw(base_size = 22)+
scale_y_continuous(expression("Net N mineralized (µg N "*g^-1*"N)")) +
scale_x_continuous(expression("Mean flux (µg C" *O[2]* "-C "  *  g^-1*"C)")) +
stat_smooth(method = "lm", formula = y ~ x, color = 1)

#nitrate starts here
ctrl <- lmeControl(opt='optim') 
nn <-lme(net.nit ~ 1,  random=~ 1|fire, method  ="ML", control=ctrl, data=full1, na.action=na.exclude)
summary(nn)

nn1 <-lme(net.nit ~ flux.c,  random=~ 1|fire, method  ="ML", control=ctrl, data=full1, na.action=na.exclude)
summary(nn1)
anova(nn, nn1)

####not significant
ggplot(full, aes(y = net.nit, x = mean.flux)) +
geom_point() +
theme_bw(base_size = 30)+
ylab("Net Nitrate mineralized (µg N/g dry soil)") +
xlab(expression("Mean C" *O[2]* " flux")) +
stat_smooth(method = "lm", formula = y ~ x, size = 2, se = FALSE)
```

Analysis soil age x mineralization
both variables are normally dist
not significant
```{r}
ggplot()+
  geom_histogram(data=full, aes(net.din))
ggplot()+
  geom_histogram(data=full, aes(soil.age))

ctrl <- lmeControl(opt='optim') 
m1 <-lme(net.din ~ soil.age,  random=~ 1|fire, method  ="ML", control=ctrl, data=full, na.action=na.exclude)
summary(m1)
anova(m1)

m2 <-lme(net.din ~ 1,  random=~ 1|fire, method  ="ML", control=ctrl, data=full, na.action=na.exclude)
summary(m2)
anova(m1, m2)

m3 <-lme(net.din ~ log1p(soil.age),  random=~ 1|fire, method  ="ML", control=ctrl, data=full, na.action=na.exclude)
summary(m3)
anova(m1, m3)

ggplot(full, aes(x = soil.age, y = net.din)) +
geom_point(size = 2) +
theme_bw(base_size = 22)+
geom_abline(slope = 0,intercept = 0) +
scale_y_continuous(expression("Net N mineralized (µg N "*g^-1*"N)")) +
xlab(expression("Bulk soil delt"*a^14*"C") ) 
```

soil age and mineralization per g N
```{r}
ctrl <- lmeControl(opt='optim') 
na1 <-lme(min.n ~ soil.age,  random=~ 1|fire, method  ="ML", control=ctrl, data=full1, na.action=na.exclude)
summary(na1)
anova(na1)

na2 <-lme(min.n ~ 1,  random=~ 1|fire, method  ="ML", control=ctrl, data=full1, na.action=na.exclude)
anova(na2)
anova(na1, na2)

na3 <-lme(min.n + min.n^2~ soil.age,  random=~ 1|fire, method  ="ML", control=ctrl, data=full1, na.action=na.exclude)
anova(na3)
plot(na3)

ggplot(full1, aes(x = soil.age, y = min.n)) +
geom_point(size = 2) +
theme_bw(base_size = 22)+
scale_y_continuous(expression("Net N mineralized (µg N "*g^-1*"N)")) +
xlab(expression("Bulk soil "*paste(Delta^{14}, "C (‰)")))  
```

variance structure for age and mineralization example code
Look at Zuur book
```{r}
model=lme(data=data, y~ x* z,  weights=varComb(varExp(form=~z), varIdent(form=~1|x)),random=~1|project/fire, na.action=na.omit, method="REML")
```

soil age and microbial biomass
```{r}
ggplot()+
  geom_histogram(data=full, aes(meanmb))
ggplot()+
  geom_histogram(data=full, aes(soil.age))

null <-lmer(mb.c ~ 1 + (1|fire), data=full1, na.action=na.exclude)
summary(null)
anova(null)
r.squaredGLMM(null)

mb <-lmer(mb.c ~ soil.age + (1|fire), data=full1, na.action=na.exclude)
summary(mb)
anova(null, mb)
anova(mb)
r.squaredGLMM(mb)
plot(mb)

ggplot(full1, aes(x = soil.age, y = mb.c)) +
geom_point(size = 2) +
theme_bw(base_size = 22)+
geom_abline(slope = 0,intercept = 0) +
scale_y_continuous(expression("Microbial C (µg C "*g^-1*"C)")) +
xlab(expression("Bulk soil "*paste(Delta^{14}, "C (‰)"))) +
stat_smooth(method = "lm", formula = y ~ x, color=1)
```

soil age and microbial activity
```{r}
ggplot()+
  geom_histogram(data=full1, aes(flux.mb))
ggplot()+
  geom_histogram(data=full1, aes(soil.age))

act1 <-lmer(flux.mb ~ 1 + (1|fire), data=full1, na.action=na.exclude)
summary(act1)
anova(act1)
r.squaredGLMM(act1)

act.age <-lmer(flux.mb ~ soil.age + (1|fire), data=full1, na.action=na.exclude)
summary(act.age)
anova(act1, act.age)
anova(act.age)
r.squaredGLMM(act.age)
plot(act.age)

act.age1 <-lmer(log(flux.mb) ~ soil.age + (1|fire), data=full1, na.action=na.exclude)
summary(act.age1)
anova(act.age, act.age1)
r.squaredGLMM(act.age1)
plot(act.age1)

ggplot(full1, aes(x = soil.age, y = log(flux.mb))) +
geom_point(size = 2) +
theme_bw(base_size = 20)+
scale_y_continuous(expression("Microbial C respiration mass ratio")) +
xlab(expression("Bulk soil "*paste(Delta^{14}, "C (‰)"))) +
stat_smooth(method = "lm", formula = y ~ x, color=1)

#(µg C" *O[2]* "-C "*g^-1*"C µg C" *g^-1*""
```

mineralization and microbial activity
not significant
makes sense flux not related to mineralization as well
```{r}
minmb <-lmer(net.din ~ 1 + (1|fire), data=full1, na.action=na.exclude)
summary(minmb)
minmb1 <-lmer(net.din ~ flux.mb + (1|fire), data=full1, na.action=na.exclude)
summary(minmb1)
anova(minmb, minmb1)
anova(minmb1)
r.squaredGLMM(minmb1)
```

microbes and mineralization
```{r}
ggplot()+
  geom_histogram(data=full, aes(meanmb))
ggplot()+
  geom_histogram(data=full, aes(net.din))

mbmin <-lmer(net.din ~ 1 + (1|fire), data=full, na.action=na.exclude)
summary(mbmin)
mbmin1 <-lmer(net.din ~ meanmb + (1|fire), data=full, na.action=na.exclude)
summary(mbmin1)
anova(mbmin, mbmin1)
anova(mbmin1)
r.squaredGLMM(mbmin1)

ggplot(full, aes(y = net.din, x = meanmb)) +
geom_point(size = 2) +
theme_bw(base_size = 22)+
scale_x_continuous(expression("Microbial C (µg C "*g^-1*"C)")) +
scale_y_continuous(expression("Net N mineralized (µg N "*g^-1*"N)")) +
stat_smooth(method = "lm", formula = y ~ x, color=1)
```

soil age x percent carbon graph
```{r}
carbon <-lmer(meanc ~ 1 + (1|fire), data=full2, na.action=na.exclude)
summary(carbon)
carbon1 <-lmer(meanc ~ soil.age + (1|fire), data=full, na.action=na.exclude)
summary(carbon1)
anova(carbon, carbon1)
anova(carbon1)
r.squaredGLMM(carbon1)

ggplot(full, aes(x = soil.age, y = meanc)) +
geom_point(size = 2) +
theme_bw(base_size = 30)+
geom_abline(slope = 0,intercept = 0) +
ylab("Carbon (%)") +
xlab(expression("Bulk soil "*paste(Delta^{14}, "C (‰)"))) +
stat_smooth(method = "lm", formula = y ~ x, color=1)
```

soil age x CN ratio graph
```{r}
ggplot()+
  geom_histogram(data=full, aes(C.N))

carbon <-lmer(C.N ~ 1 + (1|fire), data=full, na.action=na.exclude)
summary(carbon)
carbon1 <-lmer(C.N ~ soil.age + (1|fire), data=full, na.action=na.exclude)
summary(carbon1)
anova(carbon, carbon1)
anova(carbon1)
r.squaredGLMM(carbon1)
plot(carbon1)

carbon2 = lmer(log(C.N) ~ soil.age + (1|fire), data=full, na.action=na.exclude)
summary(carbon1)
anova(carbon1, carbon2)
anova(carbon2)
r.squaredGLMM(carbon2)
plot(carbon2)
      
ggplot(full, aes(x = soil.age, y = C.N)) +
geom_point(size = 2) +
theme_bw(base_size = 30)+
ylab("C/N ratio") +
xlab(expression("Bulk soil "*paste(Delta^{14}, "C (‰)"))) 
```

```{r}
min.cn <-lmer(min.n ~ C.N + (1|fire), data=full2, na.action=na.exclude)
min.cn1 <-lmer(min.n ~ 1 + (1|fire), data=full2, na.action=na.exclude)
anova(min.cn, min.cn1)
anova(min.cn)

ggplot(full1, aes(y = min.n, x = C.N)) +
geom_point(size = 2) +
theme_bw(base_size = 30)+
xlab("C/N ratio") +
scale_y_continuous(expression("Net N mineralized (µg N "*g^-1*"N)")) 

min.bs <-lmer(min.n ~ density_picea_mariana + (1|fire), data=full2, na.action=na.exclude)
min.bs1 <-lmer(min.n ~ 1 + (1|fire), data=full2, na.action=na.exclude)
anova(min.bs, min.bs1)
anova(min.bs)

ggplot(full2, aes(y = min.n, x = density_picea_mariana)) +
geom_point(size = 2) +
theme_bw(base_size = 30)+
xlab("BS density") +
scale_y_continuous(expression("Net N mineralized (µg N "*g^-1*"N)"))
```

flux x respiration age graph
```{r}
ggplot()+
  geom_histogram(data=full, aes(mean.flux))
ggplot()+
  geom_histogram(data=full, aes(res.age))

res1 <-lmer(res.age ~ 1 + (1|fire), data=full1, na.action=na.exclude)
summary(res1)
res2 <-lmer(res.age ~ flux.c + (1|fire), data=full1, na.action=na.exclude)
summary(res2)
anova(res1, res2)
anova(res2)
r.squaredGLMM(res2)
res3 <-lmer(res.age ~ log(mean.flux) + (1|fire), data=full, na.action=na.exclude)
summary(res3)
anova(res2, res3)

ggplot(full1, aes(x = flux.c, y = res.age)) +
geom_point(size = 4) +
theme_bw(base_size = 22)+
scale_x_continuous(expression("Mean flux (µg C" *O[2]* "-C "  *  g^-1*"C)")) +
ylab(expression("Respired "*paste(Delta^{14}, "C (‰)"))) +
stat_smooth(method = "lm", formula = y ~ x, color=1)
```

flux g C x respiration age graph
same as above
```{r}
res1 <-lmer(res.age ~ 1 + (1|fire), data=full1, na.action=na.exclude)
summary(res1)
res2 <-lmer(res.age ~ flux.c + (1|fire), data=full1, na.action=na.exclude)
summary(res2)
anova(res1, res2)
anova(res2)
r.squaredGLMM(res2)
plot(res2)

ggplot(full1, aes(x = flux.c, y = res.age)) +
geom_point(size = 4) +
theme_bw(base_size = 22)+
scale_x_continuous(expression("Mean flux (µg C" *O[2]* "-C "  *  g^-1*"C)")) +
ylab(expression("Respired "*paste(Delta^{14}, "C (‰)"))) +
stat_smooth(method = "lm", formula = y ~ x, color=1)
```

depth and moisture are .55 correlation so just need one in model. additive model res ~ flux + moisture is model
```{r}
site.chr = read.csv("NWT_site_charac_combustion.csv")
res.site = merge(full1, site.chr, by = c("plot"))

res.age <-lmer(res.age ~ moisture_class * org_layer_depth_transect + (1|fire), data=res.site, na.action=na.exclude)
anova(res.age)
res.age1 <-lmer(res.age ~ moisture_class + org_layer_depth_transect + (1|fire), data=res.site, na.action=na.exclude)
anova(res.age, res.age1)
anova(res.age1)
res.age2 <-lmer(res.age ~ 1 + (1|fire), data=res.site, na.action=na.exclude)
anova(res.age1, res.age2)
anova(res.age1)
r.squaredGLMM(res.age1)
plot(res.age1)

m.org <-lmer( org_layer_depth_transect~ moisture_class + (1|fire), data=res.site, na.action=na.exclude)
r.squaredGLMM(m.org)

res.site$moisture<-factor(res.site$moisture, levels= c("mesic-subxeric","mesic","mesic-subhygric", "subhygric" ))

ggplot(res.site, aes(x = flux.c, y = res.age, color = moisture_class)) +
geom_point(size = 2) +
theme_bw(base_size = 22)+
scale_fill_brewer(palette = "RdYlBu") + 
scale_color_brewer(palette = "RdYlBu") +
scale_x_continuous(expression("Mean flux (µg C" *O[2]* "-C "  *  g^-1*"C)")) +
ylab(expression("Respired "*paste(Delta^{14}, "C (‰)"))) +
  geom_smooth(method = glm, formula = y ~ x, se = FALSE)
```


```{r}
ggplot(full1, aes(x = flux.c, y = res.age)) +
geom_point(size = 4) +
theme_bw(base_size = 22)+
scale_x_continuous(expression("Mean flux (µg C" *O[2]* "-C "  *  g^-1*"C)")) +
ylab(expression("Respired "*paste(Delta^{14}, "C (‰)"))) +
stat_smooth(method = "lm", formula = y ~ x, color=1)
```

soil age and respiration age for transit time and C cycling
```{r}
ggplot(full, aes(x = soil.age, y = res.age)) +
geom_point(size = 2) +
theme_bw(base_size = 22)+
geom_abline(slope = 1,intercept = 0) +
xlab(expression("Bulk soil "*paste(Delta^{14}, "C (‰)"))) +
ylab(expression("Respired "*paste(Delta^{14}, "C (‰)"))) 
```

microbial biomass over time graph
```{r}
mb.nitro$doi=as.factor(mb.nitro$doi)
se<- function(x) sqrt(var(x)/4)

mb.avr <- aggregate(mbc ~ doi, data=mb.nitro, FUN=mean)
mb.se <- aggregate(mbc ~ doi, data=mb.nitro, FUN=se)
mb.combo<- merge(mb.avr, mb.se, by=c("doi"))
colnames(mb.combo)=c('doi', 'mean','se')

ggplot(mb.combo, aes(x = doi, y = mean)) + 
  scale_y_continuous(expression("Microbial biomass C (µg C/g dry soil)")) +
  geom_errorbar(aes(ymax = mean + se, ymin = mean - se), width=0.25) +
  geom_point(size = 1.7) +
  theme(text = element_text(size=25),
        panel.background = element_rect(fill='white', colour='white'),
        panel.border = element_rect(fill = NA, color = "black"),
        axis.title = element_text(face = "bold",size = rel(1)),
        axis.title.y = element_text(angle=90,vjust =2),
        axis.text = element_text(size = 15),
        axis.line = element_line(colour="black"),
        axis.ticks = element_line(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position= "none",
        strip.background=element_rect(colour=NA ,fill= NA),
        strip.text = element_text(face="bold"))
```

microbes by sample to check pattern
```{r}
ggplot(mb.nitro, aes(x=doi)) +

ylab('MB biomass') + 
facet_wrap(~ sample, ncol=6) +
geom_point(aes(y=mbc)) 
```

nitrogen over time graph
```{r}
mb.nitro$doi=as.factor(mb.nitro$doi)
se<- function(x) sqrt(var(x)/4)

din.avr <- aggregate(din ~ doi, data=mb.nitro, FUN=mean)
din.se <- aggregate(din ~ doi, data=mb.nitro, FUN=se)
din.combo<- merge(din.avr, din.se, by=c("doi"))
colnames(din.combo)=c('doi', 'mean','se')

ggplot(din.combo, aes(x = doi, y = mean)) + 
  scale_y_continuous(expression("Extractable DIN (µg N/g dry soil)")) +
  xlab("Day of incubation") +
  geom_errorbar(aes(ymax = mean + se, ymin = mean - se), width=0.25) +
  geom_point(size = 1.7) +
  theme(text = element_text(size=22),
        panel.background = element_rect(fill='white', colour='white'),
        panel.border = element_rect(fill = NA, color = "black"),
        axis.title = element_text(face = "bold",size = rel(1)),
        axis.title.y = element_text(angle=90,vjust =2),
        axis.text = element_text(size = 15),
        axis.line = element_line(colour="black"),
        axis.ticks = element_line(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position= "none",
        strip.background=element_rect(colour=NA ,fill= NA),
        strip.text = element_text(face="bold"))
```

moisture and depth influence on flux
depth is significant but does it matter relationship isnt strong and is almost flat

moisture depth interaction model not significant
```{r}
site.chr = read.csv("NWT_site_charac_combustion.csv")
flux = read.csv("All_flux.csv")

flux.site = flux %>%
  group_by(plot, sample) %>%
  mutate(mean.flux = mean(flux,  na.rm = TRUE))

flux.site = merge(flux.site, site.chr, by = c("plot"))
flux.site$moisture<-factor(flux.site$moisture, levels= c("mesic-subxeric","mesic","mesic-subhygric", "subhygric" ))

flux.site = flux.site %>%
  group_by(plot, sample, mean.flux, burn, moisture, org_layer_depth_transect) %>%
  summarise(flux = mean(mean.flux,  na.rm = TRUE))

moist1 <-lmer(mean.flux ~ 1 + (1|burn), data=flux.site, na.action=na.exclude)
summary(moist1)
moist2 <-lmer(mean.flux ~ moisture + (1|burn), data=flux.site, na.action=na.exclude)
summary(moist2)
anova(moist1, moist2)

ggplot(flux.site, aes(y= mean.flux, x = moisture)) +
  geom_boxplot() +
  geom_point(data=flux.site, aes(y=mean.flux, color = moisture ),  position=position_dodge(width=0.75))+
  theme_bw(base_size = 22)+
  scale_fill_brewer(palette="RdYlBu", direction=-1)+
  scale_color_brewer(palette="RdYlBu", direction=-1) +
  xlab("Mousture class") +
  scale_y_continuous(expression("Mean flux (µg C" *O[2]* "-C "  *  g^-1*"C)")) 
depth <-lmer(mean.flux ~ 1 + (1|burn), data=flux.site, na.action=na.exclude)
summary(depth)
depth1 <-lmer(mean.flux ~ org_layer_depth_transect + (1|burn), data=flux.site, na.action=na.exclude)
summary(depth1)
anova(depth, depth1)
r.squaredGLMM(depth1)
plot(depth1)

ggplot(flux.site, aes(x = org_layer_depth_transect , y = mean.flux)) +
geom_point(size = 2) +
theme_bw(base_size = 22)+
scale_y_continuous(expression("Mean flux (µg C" *O[2]* "-C "  *  g^-1*"soil)")) +
xlab("Soil organic layer depth") +
   scale_fill_brewer(palette="RdYlBu", direction=-1)+
  scale_color_brewer(palette="RdYlBu", direction=-1) +
stat_smooth(method = "lm", formula = y ~ x, color=1)

dep.moi <-lmer(flux.c ~ org_layer_depth_transect * moisture + (1|burn), data=site.flux.all, na.action=na.exclude)
anova(dep.moi)
dep.moi1 <-lmer(flux.c ~ org_layer_depth_transect + moisture + (1|burn), data=site.flux.all, na.action=na.exclude)
anova(dep.moi, dep.moi1)
anova(dep.moi1)
```

```{r}
site.flux.all = merge(flux.site, full1, by = c("plot", "sample"))

depth <-lmer(soil.age ~ 1 + (1|burn), data=site.flux.all, na.action=na.exclude)
summary(depth)
depth1 <-lmer(soil.age ~ org_layer_depth_transect + (1|burn), data=site.flux.all, na.action=na.exclude)
summary(depth1)
anova(depth, depth1)
r.squaredGLMM(depth1)
plot(depth1)

ggplot(site.flux.all, aes(x = org_layer_depth_transect , y = soil.age)) +
geom_point(size = 2) +
theme_bw(base_size = 22)+
ylab(expression("Bulk soil "*paste(Delta^{14}, "C (‰)"))) +
xlab("Soil organic layer depth") +
stat_smooth(method = "lm", formula = y ~ x, color=1)
```

moisture and organic layer depth with mineralization 
same things as with C flux
same as C. Moisture not sig; organic layer depth is
also fit interaction model only org deoth sig
```{r}
moi.n <-lmer( min.n ~ moisture * org_layer_depth_transect + (1|burn), data= site.flux.all, na.action=na.exclude)
moi.n1 <-lmer( min.n ~ moisture + org_layer_depth_transect + (1|burn), data= site.flux.all, na.action=na.exclude)
anova(moi.n, moi.n1)
anova(moi.n1)

moi.n2 <-lmer( min.n ~ org_layer_depth_transect + (1|burn), data= site.flux.all, na.action=na.exclude)
anova(moi.n1, moi.n2)
moi.n3 <-lmer( min.n ~ 1 + (1|burn), data= site.flux.all, na.action=na.exclude)
anova(moi.n3, moi.n2)
r.squaredGLMM(moi.n2)
plot(moi.n2)

ggplot(site.flux.all, aes(x = org_layer_depth_transect , y = min.n)) +
geom_point(size = 2) +
theme_bw(base_size = 22)+
scale_y_continuous(expression("Net N mineralized (µg N "*g^-1*"N)")) +
xlab("Soil organic layer depth") +
stat_smooth(method = "lm", formula = y ~ x, color=1)

moist1 <-lmer(min.n ~ 1 + (1|burn), data=site.flux.all, na.action=na.exclude)
summary(moist1)
moist2 <-lmer(min.n ~ moisture + (1|burn), data=site.flux.all, na.action=na.exclude)
summary(moist2)
anova(moist1, moist2)
anova(moist2)

site.flux.all$moisture<-factor(site.flux.all$moisture, levels= c("mesic-subxeric","mesic","mesic-subhygric", "subhygric" ))

ggplot(site.flux.all, aes(y= min.n, x = moisture)) +
  geom_boxplot() +
  geom_point(data=site.flux.all, aes(y=min.n, color = moisture ),  position=position_dodge(width=0.75))+
  theme_bw(base_size = 22)+
  scale_fill_brewer(palette="RdYlBu", direction=-1)+
  scale_color_brewer(palette="RdYlBu", direction=-1) +
  xlab("Mousture class") +
scale_y_continuous(expression("Net N mineralized (µg N "*g^-1*"N)")) 
```

nitrogen doesn change with soil age; not sig
```{r}
n <-lmer(meann ~ 1 + (1|fire), data=full, na.action=na.exclude)

n1 <-lmer(meanc ~ soil.age + (1|fire), data=full, na.action=na.exclude)
anova(n1)
anova(n, n1)

ggplot(full, aes(x = soil.age, y = meann)) +
geom_point(size = 2) +
theme_bw(base_size = 30)+
geom_abline(slope = 0,intercept = 0) +
ylab("Nitrogen (%)") +
xlab(expression("Bulk soil "*paste(Delta^{14}, "C (‰)"))) 
```


flux over time by g C with site characteristics
```{r}
cn = read.csv("CN.csv")
flux = read.csv("All_flux.csv")
flux.cn = merge(flux, cn, by = c("sample"))

c1 = flux.cn %>% 
  group_by(sample, plot) %>% 
  summarize(meanc = mean(carbon, na.rm=TRUE))  
 
n1 = flux.cn %>% 
  group_by(sample, plot) %>% 
  summarize(meann = mean(nitrogen, na.rm=TRUE)) 
 
meancn = merge(n1, c1, by = c("sample", "plot"))
meancn = meancn %>% 
  mutate(C.N = meanc/meann)

flux.cn = merge(flux, meancn, by = c("sample"))

#per C
full1 = flux.cn %>%
  group_by(sample, DOI) %>%
  mutate(flux.c = flux/meanc)

site.chr = read.csv("NWT_site_charac_combustion.csv")

flux.and.site = select(full1, c("sample", "DOI", "moisture", "plot.x", "flux.c")) %>% 
  rename(plot = plot.x)

full2 = merge(flux.and.site, site.chr, by = c("plot"))
```


DOI and moisture g C flux analysis
DOI sig not moiusture
```{r}
x1 <-lmer(flux.c ~ DOI * moisture + (1|burn)+(1|sample), data= full2, na.action=na.exclude)
anova(x1)

x2 <-lmer(flux.c ~ DOI + moisture + (1|burn)+(1|sample), data= full2, na.action=na.exclude)
anova(x1, x2)
anova(x2)

x3 <-lmer(flux.c ~ DOI + (1|burn)+(1|sample), data= full2, na.action=na.exclude)
anova(x3, x2)
anova(x3)

x4 <-lmer(flux.c ~ 1 + (1|burn)+(1|sample), data= full2, na.action=na.exclude)
anova(x3, x4)

full2$moisture<-factor(full2$moisture, levels= c("mesic-subxeric","mesic","mesic-subhygric", "subhygric" ))

ggplot(full2, aes(x = DOI , y = flux.c, color =moisture)) +
geom_point(size = 2) +
theme_bw(base_size = 22)+
scale_fill_brewer(palette = "RdYlBu") + 
  scale_color_brewer(palette = "RdYlBu") +
  scale_y_continuous(expression("Flux (µg C" *O[2]* "-C "*g^-1*"C)")) +
xlab("DAY") +
  geom_smooth(formula=y~x, method="glm", method.args=list(family=gaussian(link="log"))) 

```

DOI flux by sample
they all look more or less linear
```{r}
full2$moisture<-factor(full2$moisture, levels= c("mesic-subxeric","mesic","mesic-subhygric", "subhygric" ))

ggplot(full2, aes(x = DOI , y = flux.c, color =moisture)) +
geom_point(size = 2) +
theme_bw(base_size = 10)+
scale_fill_brewer(palette = "RdYlBu") + 
  scale_color_brewer(palette = "RdYlBu") +
  scale_y_continuous(expression("Flux (µg C" *O[2]* "-C "*g^-1*"C)")) +
xlab("DAY") +
  geom_smooth(formula=y~x, method="glm", method.args=list(family=gaussian(link="log"))) +
  facet_wrap(~ sample) 
  
```

